New CCA sardines, Sept 2022

### 2022-10-28 NewCCASardines.Rmd

---
title: "New CCA sardines"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)  
library(atlantisom)
library(ggthemes)
library(FSA)

```

A test run for sardines with the updated California Current model, run 44:

```{r full-test, message=FALSE, warning=FALSE, eval=FALSE}

CCom <- atlantisom::om_init(here("config/CCConfigv4.R"))

@@

CCom_sard_ind <- atlantisom::om_index(usersurvey = here("config/sardinesurvey.R"), 
                           userfishery = here("config/sardinefishery.R"),
                           omlist_ss = CCom_sard, 
                           n_reps = 1, 
                           save = TRUE)

CCom_sard_comp <- atlantisom::om_comps(usersurvey = here("config/sardinesurvey.R"), 
                           userfishery = here("config/sardinefishery.R"),
                           omlist_ss = CCom_sard, 
                           n_reps = 1, 
                           save = TRUE)

```

@@

usersurvey = here("config/sardinesurvey.R")

@@

#this is om_index

#one script for dimension parameters to be used in multiple functions
  source("config/omdimensions.R", local = TRUE)

@@

    #biomass based fishery independent survey index
    # this uses result$biomass_ages to sample biomass directly, no need for wt@age est
    survey_B <- atlantisom::create_survey(dat = omlist_ss$truebio_ss,
                                          time = survtime,
                                          species = survspp,
                                          boxes = survboxes,
                                          effic = surveffic,
                                          selex = survselex)

    # call sample_survey_biomass with a bunch of 1000s for weight at age
    # in the code it multiplies atoutput by wtatage/1000 so this allows us to use
    # biomass directly
    wtage <- data.frame(species=rep(names(age_classes), n_age_classes),
                        agecl=unlist(sapply(n_age_classes,seq)),
                        wtAtAge=rep(1000.0,sum(n_age_classes)))

    # this is the step to repeat n_reps time if we want different realizations
    # of the same survey design specified above; only observation error differs
    # using the census cv of 0 will produce identical reps!
    survObsBiomB <- list()
    for(i in 1:n_reps){
      survObsBiomB[[i]] <- atlantisom::sample_survey_biomass(survey_B, surv_cv, wtage)
    }

    #save survey indices, takes a long time to generate with lots of reps/species
    if(save){
      saveRDS(survObsBiomB, file.path(d.name, paste0(scenario.name, "_",
                                                     survey.name, "surveyB.rds")))
    }

@@

  #configure the fishery, a default is in config/fisherycensus.R
  #fishery configuration can specify only area and time of observation
  #fishery species inherited from omlist_ss
  #this is total catch not by fleet, so only one "fishery"
  source(userfishery, local = TRUE)

  #we are not currently subsetting fishery catch because we cannot correct catch.nc
  #  instead the catch in biomass from catch.txt is read in for the index
  #  we do not apply any cv to this, but we could this way (default cv=0)

  fishObsCatchB <- list()
  for(i in 1:n_reps){
    fishObsCatchB[[i]] <- atlantisom::sample_fishery_totcatch(omlist_ss$truecatchbio_ss, fish_cv)
  }

  if(save){
    saveRDS(fishObsCatchB, file.path(d.name, paste0(scenario.name, "_",
                                                    fishery.name, "fishCatch.rds")))
  }

  indices <- list("survObsBiomB" = survObsBiomBs,
                  "fishObsCatchB" = fishObsCatchB)

  return(indices)
}

```

@@

#this is om_comps

 #one script for dimension parameters to be used in multiple functions
  source("config/omdimensions.R", local = TRUE)

@@

    #numbers based fishery independent survey for age and length comps
    # same user specifications as indices
    survey_N <- atlantisom::create_survey(dat = omlist_ss$truenums_ss,
                                          time = survtime,
                                          species = survspp,
                                          boxes = survboxes,
                                          effic = surveffic,
                                          selex = survselex.agecl)

    #Sample fish for age composition
    # if we want replicates for obs error this sample function will generate them
    age_comp_data <- list()
    for(i in 1:n_reps){
      age_comp_data[[i]] <- atlantisom::sample_fish(survey_N, surveffN)
    }

    # save age comps
    if(save){
      saveRDS(age_comp_data, file.path(d.name, paste0(scenario.name, "_",
                                                      survey.name, "survObsAgeComp.rds")))
    }

    #weights needed for weight at age and length comp calcs
    # aggregate true resn per survey design
    survey_aggresn <- atlantisom::aggregateDensityData(dat = omlist_ss$trueresn_ss,
                                                       time = survtime,
                                                       species = survspp,
                                                       boxes = survboxes)

    # aggregate true structn per survey design
    survey_aggstructn <- atlantisom::aggregateDensityData(dat = omlist_ss$truestructn_ss,
                                                          time = survtime,
                                                          species = survspp,
                                                          boxes = survboxes)

    #dont sample these, just aggregate them using median
    structnss <- atlantisom::sample_fish(survey_aggstructn, surveffN, sample = FALSE)

@@

    #this is all input into the length function, replicates follow age comp reps
    #  separating the length comps from the weight at age here
    survey_lenwt <- list()
    survObsLenComp <- list()
    survObsWtAtAge <- list()

    for(i in 1:n_reps){
      survey_lenwt[[i]] <- atlantisom::calc_age2length(structn = structnss,
                                                       resn = resnss,
                                                       nums = age_comp_data[[i]],
                                                       biolprm = omlist_ss$biol,
                                                       fgs = omlist_ss$funct.group_ss,
                                                       maxbin = maxbin,
                                                       CVlenage = lenage_cv,
                                                       remove.zeroes=TRUE)

@@

    if(save){
      saveRDS(survObsLenComp, file.path(d.name, paste0(scenario.name, "_",
                                                       survey.name, "survObsLenComp.rds")))
      saveRDS(survObsWtAtAge, file.path(d.name, paste0(scenario.name, "_",
                                                       survey.name, "survObsWtAtAge.rds")))
    }
    # add each survey to master list objects for survey data
    age_comp_datas[[survey.name]] <- age_comp_data
    survObsLenComps[[survey.name]] <- survObsLenComp
    survObsWtAtAges[[survey.name]] <- survObsWtAtAge

  }

  #now do fishery comps
  # user options for fishery--default is a census with mid-year sample
  # only one fishery, but multiple fleets possible within it
  source(userfishery, local = TRUE)

  #fishery catch at age each observed timestep summed over observed polygons
  # catch at age by area and timestep
  catch_numbers <-  atlantisom::create_fishery_subset(dat = omlist_ss$truecatchnum_ss,
                                                      time = fishtime,
                                                      species = survspp,
                                                      boxes = fishboxes)

  # if we want replicates for obs error this sample function will generate them
  catch_age_comp <- list()
  for(i in 1:n_reps){
    catch_age_comp[[i]] <- atlantisom::sample_fish(catch_numbers, fisheffN)
  }

  # save fishery age comps
  if(save){
    saveRDS(catch_age_comp, file.path(d.name, paste0(scenario.name, "_",
                                                     fishery.name, "fishObsAgeComp.rds")))
  }

  #Get catch weights for length comp calc
  # aggregate true resn per fishery subset design
  catch_aggresnss <- atlantisom::aggregateDensityData(dat = omlist_ss$trueresn_ss,
                                                      time = fishtime,
                                                      species = survspp,
                                                      boxes = fishboxes)

  # aggregate true structn fishery subsetdesign
  catch_aggstructnss <- atlantisom::aggregateDensityData(dat = omlist_ss$truestructn_ss,
                                                         time = fishtime,
                                                         species = survspp,
                                                         boxes = fishboxes)

  #dont sample these, just aggregate them using median
  catch_structnss <- atlantisom::sample_fish(catch_aggstructnss, fisheffN, sample = FALSE)

@@

  # these fishery lengths and weight at age are each output timestep
  #same structure as above for surveys, replicates follow age comp reps
  #  separating the length comps from the weight at age here
  fishery_lenwt <- list()
  fishObsLenComp <- list()
  fishObsWtAtAge <- list()

  for(i in 1:n_reps){
    fishery_lenwt[[i]] <- atlantisom::calc_age2length(structn = catch_structnss,
                                                      resn = catch_resnss,
                                                      nums = catch_age_comp[[i]],
                                                      biolprm = omlist_ss$biol,
                                                      fgs = omlist_ss$funct.group_ss,
                                                      maxbin = maxbin,
                                                      CVlenage = lenage_cv,
                                                      remove.zeroes=TRUE)

@@

  if(save){
    saveRDS(fishObsLenComp, file.path(d.name, paste0(scenario.name, "_",
                                                     fishery.name, "fishObsLenComp.rds")))
    saveRDS(fishObsWtAtAge, file.path(d.name, paste0(scenario.name, "_",
                                                     fishery.name, "fishObsWtAtAge.rds")))
  }

  if(!is.null(omlist_ss$truenumsage_ss)){
    #numbers based fishery independent survey for age and length comps
    #allows for mulitple surveys
    annage_comp_datas <- list()

@@

      # same user specifications as indices
      survey_annageN <- atlantisom::create_survey(dat = omlist_ss$truenumsage_ss,
                                                  time = survtime,
                                                  species = survspp,
                                                  boxes = survboxes,
                                                  effic = surveffic,
                                                  selex = survselex)
      #Sample fish for age composition
      # if we want replicates for obs error this sample function will generate them
      annage_comp_data <- list()
      for(i in 1:n_reps){
        annage_comp_data[[i]] <- atlantisom::sample_fish(survey_annageN, surveffN)
      }

      # save survey annual age comps
      if(save){
        saveRDS(annage_comp_data, file.path(d.name, paste0(scenario.name, "_",
                                                           survey.name, "survObsFullAgeComp.rds")))
      }
      annage_comp_datas[[survey.name]] <- annage_comp_data
    }

  }else{annage_comp_datas <- NULL}

  if(!is.null(omlist_ss$truecatchage_ss)){
    #fishery catch at age each observed timestep summed over observed polygons
    # catch at age by area and timestep
    catch_annagenumbers <-  atlantisom::create_fishery_subset(dat = omlist_ss$truecatchage_ss,
                                                        time = fishtime,
                                                        species = survspp,
                                                        boxes = fishboxes)

    # if we want replicates for obs error this sample function will generate them
    # WARNING THIS AGGREGATES ACROSS FLEETS
    # TODO: need to change sample_fish to fix
    catch_annage_comp <- list()
    for(i in 1:n_reps){
      catch_annage_comp[[i]] <- atlantisom::sample_fish(catch_annagenumbers, fisheffN)
    }

    # save fishery annual age comps
    if(save){
    saveRDS(catch_annage_comp, file.path(d.name, paste0(scenario.name,"_",
                                                        fishery.name, "fishObsFullAgeComp.rds")))
    }
  }else{catch_annage_comp <- NULL}

  # call interpolate weight at age function to get survObsFullWtAtAge
  if(!is.null(omlist_ss$truenumsage_ss)){
    interp_survWtAtAges <- list()
    for (s in usersurvey)
    {
      source(s, local = TRUE)

      interp_survWtAtAge <- list()
      for(i in 1:n_reps){
        interp_survWtAtAge[[i]] <- calc_avgwtstage2age(wtagecl = survObsWtAtAges[[survey.name]][[i]],
                                                       annages = omlist_ss$truenumsage_ss,
                                                       fgs = omlist_ss$funct.group_ss)
      }
      if(save){
        saveRDS(interp_survWtAtAge, file.path(d.name, paste0(scenario.name, "_",
                                                             survey.name, "survObsFullWtAtAge.rds")))
      }
      interp_survWtAtAges[[survey.name]] <- interp_survWtAtAge
    }
  }else{interp_survWtAtAges <- NULL}

  # do we want fishery average weight at true age too? why not
  # call interpolate weight at age function to get fishObsFullWtAtAge
  # WARNING currently aggregates out fleet info, but no fleets in aggregate wtage
  if(!is.null(omlist_ss$truecatchage_ss)){
    interp_fishWtAtAge <- list()
    for(i in 1:n_reps){
      interp_fishWtAtAge[[i]] <- calc_avgwtstage2age(wtagecl = fishObsWtAtAge[[i]],
                                                     annages = omlist_ss$truecatchage_ss,
                                                     fgs = omlist_ss$funct.group_ss)
    }
    if(save){
      saveRDS(interp_fishWtAtAge, file.path(d.name, paste0(scenario.name,"_",
                                                           fishery.name, "fishObsFullWtAtAge.rds")))
    }
  }else{interp_fishWtAtAge <- NULL}

  comps <- list("survObsAgeComp" = age_comp_datas,
                "survObsLenComp" = survObsLenComps,
                "survObsWtAtAge" = survObsWtAtAges,
                "fishObsAgeComp" = catch_age_comp,
                "fishObsLenComp" = fishObsLenComp,
                "fishObsWtAtAge" = fishObsWtAtAge,
                "survObsFullAgeComp" = annage_comp_datas,
                "fishObsFullAgeComp" = catch_annage_comp,
                "survObsFullWtAtAge" = interp_survWtAtAges,
                "fishObsFullWtAtAge" = interp_fishWtAtAge
                )

  return(comps)
}

```

@@

#read time series data
survObsBiom <- readRDS(file.path(d.name, paste0(scenario.name,
                                                "_",
                                                survey.name,
                                                "surveyB.rds")))

@@

plotB <-ggplot() +
  geom_line(data=survObsBiom, aes(x=time/stepperyr,y=atoutput, color="survey Biomass"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotB +
  facet_wrap(~species, scales="free")

```

#### Catch time series
```{r catchind-1}
#read time series data
catchbio_ss <- readRDS(file.path(d.name, paste0(scenario.name,
                                                "_",
                                                fishery.name, "fishCatch.rds")))

@@

plotC <-ggplot() +
  geom_line(data=catchbio_ss, aes(x=time/365,y=atoutput, color="observed Catch"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotC +
  facet_wrap(~species, scales="free")

```

@@

#length comps
len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name,
                                                "_",
                                                survey.name, "survObsLenComp.rds")))
fish_len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name,
                                                "_",
                                                fishery.name,"fishObsLenComp.rds")))

@@

#add this to om_indices function so that this has years when read in
fish_len_comp_data$time <- as.integer(floor(fish_len_comp_data$time/fstepperyr))

@@

  lfplot <- ggplot(len, aes(upper.bins)) +
    geom_bar(aes(weight = atoutput)) +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          len$species))

  lfplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")

```

@@

#read in comp data
age_comp_data <- readRDS(file.path(d.name, paste0(scenario.name,
                                                "_",
                                                survey.name, "survObsAgeComp.rds")))
age_comp_data <- age_comp_data[[1]]

@@

Natageplot <- ggplot(Natage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Natage$species))

  Natageplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
```

@@

wtage <- readRDS(file.path(d.name, paste0(scenario.name,
                                                "_",
                                                survey.name, "survObsWtAtAge.rds")))
wtage <- wtage[[1]]

@@

wageplot + facet_wrap(c("species"), scales="free_y")
```

@@

#read in comp data
fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name,
                                                "_",
                                                fishery.name, "fishObsAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

#add this to om_indices function so that this has years when read in
fish_age_comp$time <- fish_age_comp$time/fstepperyr

@@

Natageplot <- ggplot(Natage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Natage$species))

  Natageplot + facet_wrap(~time, ncol=6, scales="free_y")
```

@@

>>>>

---
title: "New CCA sardines, Sept 2022"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)
library(atlantisom)
library(ggthemes)
library(FSA)
```

A test run for sardines with the updated California Current model, September 2022:

```{r full-test, message=FALSE, warning=FALSE, eval=FALSE}
CCom <- atlantisom::om_init(here("config/CCConfigSep22.R"))

@@

CCom_sard_ind <- atlantisom::om_index(
  usersurvey = here("config/sardinesurvey.R"),
  userfishery = here("config/sardinefishery.R"),
  omlist_ss = CCom_sard,
  n_reps = 1,
  save = TRUE
)

CCom_sard_comp <- atlantisom::om_comps(
  usersurvey = here("config/sardinesurvey.R"),
  userfishery = here("config/sardinefishery.R"),
  omlist_ss = CCom_sard,
  n_reps = 1,
  save = TRUE
)
```

@@

usersurvey <- here("config/sardinesurvey.R")

@@

# this is om_index

# one script for dimension parameters to be used in multiple functions
source("config/omdimensions.R", local = TRUE)

###############################################
n_reps <- 1 # not sure about it, used the value from line 31
save <- FALSE # Sarah already provided output data
###############################################

@@

  # biomass based fishery independent survey index
  # this uses result$biomass_ages to sample biomass directly, no need for wt@age est
  survey_B <- atlantisom::create_survey(
    dat = omlist_ss$truebio_ss,
    time = survtime,
    species = survspp,
    boxes = survboxes,
    effic = surveffic,
    selex = survselex
  )

  # call sample_survey_biomass with a bunch of 1000s for weight at age
  # in the code it multiplies atoutput by wtatage/1000 so this allows us to use
  # biomass directly
  wtage <- data.frame(
    species = rep(names(age_classes), n_age_classes),
    agecl = unlist(sapply(n_age_classes, seq)),
    wtAtAge = rep(1000.0, sum(n_age_classes))
  )

  # this is the step to repeat n_reps time if we want different realizations
  # of the same survey design specified above; only observation error differs
  # using the census cv of 0 will produce identical reps!
  survObsBiomB <- list()
  for (i in 1:n_reps) {
    survObsBiomB[[i]] <- atlantisom::sample_survey_biomass(survey_B, surv_cv, wtage)
  }

  # save survey indices, takes a long time to generate with lots of reps/species
  if (save) {
    saveRDS(survObsBiomB, file.path(d.name, paste0(
      scenario.name, "_",
      survey.name, "surveyB.rds"
    )))
  }

@@

# configure the fishery, a default is in config/fisherycensus.R
# fishery configuration can specify only area and time of observation
# fishery species inherited from omlist_ss
# this is total catch not by fleet, so only one "fishery"

##################################################
# Use information from lines 29 and 35
userfishery <- here("config/sardinefishery.R")
##################################################
source(userfishery, local = TRUE)

# we are not currently subsetting fishery catch because we cannot correct catch.nc
#  instead the catch in biomass from catch.txt is read in for the index
#  we do not apply any cv to this, but we could this way (default cv=0)

fishObsCatchB <- list()
for (i in 1:n_reps) {
  fishObsCatchB[[i]] <- atlantisom::sample_fishery_totcatch(omlist_ss$truecatchbio_ss, fish_cv)
}

if (save) {
  saveRDS(fishObsCatchB, file.path(d.name, paste0(
    scenario.name, "_",
    fishery.name, "fishCatch.rds"
  )))
}

indices <- list(
  "survObsBiomB" = survObsBiomBs,
  "fishObsCatchB" = fishObsCatchB
)

#  return(indices)
# }
```

@@

# this is om_comps

# one script for dimension parameters to be used in multiple functions
source("config/omdimensions.R", local = TRUE)

@@

  # numbers based fishery independent survey for age and length comps
  # same user specifications as indices
  survey_N <- atlantisom::create_survey(
    dat = omlist_ss$truenums_ss,
    time = survtime,
    species = survspp,
    boxes = survboxes,
    effic = surveffic,
    selex = survselex.agecl
  )

  # Sample fish for age composition
  # if we want replicates for obs error this sample function will generate them
  age_comp_data <- list()
  for (i in 1:n_reps) {
    age_comp_data[[i]] <- atlantisom::sample_fish(survey_N, surveffN)
  }

  # save age comps
  if (save) {
    saveRDS(age_comp_data, file.path(d.name, paste0(
      scenario.name, "_",
      survey.name, "survObsAgeComp.rds"
    )))
  }

  # weights needed for weight at age and length comp calcs
  # aggregate true resn per survey design
  survey_aggresn <- atlantisom::aggregateDensityData(
    dat = omlist_ss$trueresn_ss,
    time = survtime,
    species = survspp,
    boxes = survboxes
  )

  # aggregate true structn per survey design
  survey_aggstructn <- atlantisom::aggregateDensityData(
    dat = omlist_ss$truestructn_ss,
    time = survtime,
    species = survspp,
    boxes = survboxes
  )

  # dont sample these, just aggregate them using median
  structnss <- atlantisom::sample_fish(survey_aggstructn, surveffN, sample = FALSE)

@@

  # this is all input into the length function, replicates follow age comp reps
  #  separating the length comps from the weight at age here
  survey_lenwt <- list()
  survObsLenComp <- list()
  survObsWtAtAge <- list()

  for (i in 1:n_reps) {
    survey_lenwt[[i]] <- atlantisom::calc_age2length(
      structn = structnss,
      resn = resnss,
      nums = age_comp_data[[i]],
      biolprm = omlist_ss$biol,
      fgs = omlist_ss$funct.group_ss,
      maxbin = maxbin,
      CVlenage = lenage_cv,
      remove.zeroes = TRUE
    )

@@

  if (save) {
    saveRDS(survObsLenComp, file.path(d.name, paste0(
      scenario.name, "_",
      survey.name, "survObsLenComp.rds"
    )))
    saveRDS(survObsWtAtAge, file.path(d.name, paste0(
      scenario.name, "_",
      survey.name, "survObsWtAtAge.rds"
    )))
  }
  # add each survey to master list objects for survey data
  age_comp_datas[[survey.name]] <- age_comp_data
  survObsLenComps[[survey.name]] <- survObsLenComp
  survObsWtAtAges[[survey.name]] <- survObsWtAtAge
}

# now do fishery comps
# user options for fishery--default is a census with mid-year sample
# only one fishery, but multiple fleets possible within it
source(userfishery, local = TRUE)

# fishery catch at age each observed timestep summed over observed polygons
# catch at age by area and timestep
catch_numbers <- atlantisom::create_fishery_subset(
  dat = omlist_ss$truecatchnum_ss,
  time = fishtime,
  species = survspp,
  boxes = fishboxes
)

# if we want replicates for obs error this sample function will generate them
catch_age_comp <- list()
for (i in 1:n_reps) {
  catch_age_comp[[i]] <- atlantisom::sample_fish(catch_numbers, fisheffN)
}

# save fishery age comps
if (save) {
  saveRDS(catch_age_comp, file.path(d.name, paste0(
    scenario.name, "_",
    fishery.name, "fishObsAgeComp.rds"
  )))
}

# Get catch weights for length comp calc
# aggregate true resn per fishery subset design
catch_aggresnss <- atlantisom::aggregateDensityData(
  dat = omlist_ss$trueresn_ss,
  time = fishtime,
  species = survspp,
  boxes = fishboxes
)

# aggregate true structn fishery subsetdesign
catch_aggstructnss <- atlantisom::aggregateDensityData(
  dat = omlist_ss$truestructn_ss,
  time = fishtime,
  species = survspp,
  boxes = fishboxes
)

# dont sample these, just aggregate them using median
catch_structnss <- atlantisom::sample_fish(catch_aggstructnss, fisheffN, sample = FALSE)

@@

# these fishery lengths and weight at age are each output timestep
# same structure as above for surveys, replicates follow age comp reps
#  separating the length comps from the weight at age here
fishery_lenwt <- list()
fishObsLenComp <- list()
fishObsWtAtAge <- list()

for (i in 1:n_reps) {
  fishery_lenwt[[i]] <- atlantisom::calc_age2length(
    structn = catch_structnss,
    resn = catch_resnss,
    nums = catch_age_comp[[i]],
    biolprm = omlist_ss$biol,
    fgs = omlist_ss$funct.group_ss,
    maxbin = maxbin,
    CVlenage = lenage_cv,
    remove.zeroes = TRUE
  )

@@

if (save) {
  saveRDS(fishObsLenComp, file.path(d.name, paste0(
    scenario.name, "_",
    fishery.name, "fishObsLenComp.rds"
  )))
  saveRDS(fishObsWtAtAge, file.path(d.name, paste0(
    scenario.name, "_",
    fishery.name, "fishObsWtAtAge.rds"
  )))
}

if (!is.null(omlist_ss$truenumsage_ss)) {
  # numbers based fishery independent survey for age and length comps
  # allows for mulitple surveys
  annage_comp_datas <- list()

@@

    # same user specifications as indices
    survey_annageN <- atlantisom::create_survey(
      dat = omlist_ss$truenumsage_ss,
      time = survtime,
      species = survspp,
      boxes = survboxes,
      effic = surveffic,
      selex = survselex
    )
    # Sample fish for age composition
    # if we want replicates for obs error this sample function will generate them
    annage_comp_data <- list()
    for (i in 1:n_reps) {
      annage_comp_data[[i]] <- atlantisom::sample_fish(survey_annageN, surveffN)
    }

    # save survey annual age comps
    if (save) {
      saveRDS(annage_comp_data, file.path(d.name, paste0(
        scenario.name, "_",
        survey.name, "survObsFullAgeComp.rds"
      )))
    }
    annage_comp_datas[[survey.name]] <- annage_comp_data
  }
} else {
  annage_comp_datas <- NULL
}

if (!is.null(omlist_ss$truecatchage_ss)) {
  # fishery catch at age each observed timestep summed over observed polygons
  # catch at age by area and timestep
  catch_annagenumbers <- atlantisom::create_fishery_subset(
    dat = omlist_ss$truecatchage_ss,
    time = fishtime,
    species = survspp,
    boxes = fishboxes
  )

  # if we want replicates for obs error this sample function will generate them
  # WARNING THIS AGGREGATES ACROSS FLEETS
  # TODO: need to change sample_fish to fix
  catch_annage_comp <- list()
  for (i in 1:n_reps) {
    catch_annage_comp[[i]] <- atlantisom::sample_fish(catch_annagenumbers, fisheffN)
  }

  # save fishery annual age comps
  if (save) {
    saveRDS(catch_annage_comp, file.path(d.name, paste0(
      scenario.name, "_",
      fishery.name, "fishObsFullAgeComp.rds"
    )))
  }
} else {
  catch_annage_comp <- NULL
}

# call interpolate weight at age function to get survObsFullWtAtAge
if (!is.null(omlist_ss$truenumsage_ss)) {
  interp_survWtAtAges <- list()
  for (s in usersurvey)
  {
    source(s, local = TRUE)

    interp_survWtAtAge <- list()
    for (i in 1:n_reps) {
      interp_survWtAtAge[[i]] <- calc_avgwtstage2age(
        wtagecl = survObsWtAtAges[[survey.name]][[i]],
        annages = omlist_ss$truenumsage_ss,
        fgs = omlist_ss$funct.group_ss
      )
    }
    if (save) {
      saveRDS(interp_survWtAtAge, file.path(d.name, paste0(
        scenario.name, "_",
        survey.name, "survObsFullWtAtAge.rds"
      )))
    }
    interp_survWtAtAges[[survey.name]] <- interp_survWtAtAge
  }
} else {
  interp_survWtAtAges <- NULL
}

# do we want fishery average weight at true age too? why not
# call interpolate weight at age function to get fishObsFullWtAtAge
# WARNING currently aggregates out fleet info, but no fleets in aggregate wtage
if (!is.null(omlist_ss$truecatchage_ss)) {
  interp_fishWtAtAge <- list()
  for (i in 1:n_reps) {
    interp_fishWtAtAge[[i]] <- calc_avgwtstage2age(
      wtagecl = fishObsWtAtAge[[i]],
      annages = omlist_ss$truecatchage_ss,
      fgs = omlist_ss$funct.group_ss
    )
  }
  if (save) {
    saveRDS(interp_fishWtAtAge, file.path(d.name, paste0(
      scenario.name, "_",
      fishery.name, "fishObsFullWtAtAge.rds"
    )))
  }
} else {
  interp_fishWtAtAge <- NULL
}

comps <- list(
  "survObsAgeComp" = age_comp_datas,
  "survObsLenComp" = survObsLenComps,
  "survObsWtAtAge" = survObsWtAtAges,
  "fishObsAgeComp" = catch_age_comp,
  "fishObsLenComp" = fishObsLenComp,
  "fishObsWtAtAge" = fishObsWtAtAge,
  "survObsFullAgeComp" = annage_comp_datas,
  "fishObsFullAgeComp" = catch_annage_comp,
  "survObsFullWtAtAge" = interp_survWtAtAges,
  "fishObsFullWtAtAge" = interp_fishWtAtAge
)

#  return(comps)
# }
```

@@

# read time series data
survObsBiom <- readRDS(file.path(d.name, paste0(
  scenario.name,
  "_",
  survey.name,
  "surveyB.rds"
)))

@@

plotB <- ggplot() +
  geom_line(
    data = survObsBiom, aes(x = time / stepperyr, y = atoutput, color = "survey Biomass"),
    alpha = 10 / 10
  ) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour = scenario.name)

plotB +
  facet_wrap(~species, scales = "free")
```

#### Catch time series
```{r catchind-1}
# read time series data
catchbio_ss <- readRDS(file.path(d.name, paste0(
  scenario.name,
  "_",
  fishery.name, "fishCatch.rds"
)))

@@

plotC <- ggplot() +
  geom_line(
    data = catchbio_ss, aes(x = time / 365, y = atoutput, color = "observed Catch"),
    alpha = 10 / 10
  ) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour = scenario.name)

plotC +
  facet_wrap(~species, scales = "free")
```

@@

# length comps
len_comp_data <- readRDS(file.path(d.name, paste0(
  scenario.name,
  "_",
  survey.name, "survObsLenComp.rds"
)))
fish_len_comp_data <- readRDS(file.path(d.name, paste0(
  scenario.name,
  "_",
  fishery.name, "fishObsLenComp.rds"
)))

@@

# add this to om_indices function so that this has years when read in
fish_len_comp_data$time <- as.integer(floor(fish_len_comp_data$time / fstepperyr))

@@

len <- filter(len_comp_data, time %in% c(55:175))

lfplot <- ggplot(len, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(
    scenario.name,
    len$species
  ))

lfplot + facet_wrap(~ time / stepperyr, ncol = 6, scales = "free_y")
```

@@

# read in comp data
age_comp_data <- readRDS(file.path(d.name, paste0(
  scenario.name,
  "_",
  survey.name, "survObsAgeComp.rds"
)))
age_comp_data <- age_comp_data[[1]]

@@

Natage <- filter(age_comp_data, time %in% c(150:270))

Natageplot <- ggplot(Natage, aes(x = agecl, y = atoutput)) +
  geom_point() +
  theme_tufte() +
  labs(subtitle = paste(
    scenario.name,
    Natage$species
  ))

Natageplot + facet_wrap(~ time / stepperyr, ncol = 6, scales = "free_y")
```

@@

wtage <- readRDS(file.path(d.name, paste0(
  scenario.name,
  "_",
  survey.name, "survObsWtAtAge.rds"
)))
wtage <- wtage[[1]]

@@

wageplot + facet_wrap(c("species"), scales = "free_y")
```

@@

# read in comp data
fish_age_comp <- readRDS(file.path(d.name, paste0(
  scenario.name,
  "_",
  fishery.name, "fishObsAgeComp.rds"
)))
fish_age_comp <- fish_age_comp[[1]]

# add this to om_indices function so that this has years when read in
fish_age_comp$time <- fish_age_comp$time / fstepperyr

@@

Natage <- filter(fish_age_comp, time %in% c(30:53))

Natageplot <- ggplot(Natage, aes(x = agecl, y = atoutput)) +
  geom_point() +
  theme_tufte() +
  labs(subtitle = paste(
    scenario.name,
    Natage$species
  ))

Natageplot + facet_wrap(~time, ncol = 6, scales = "free_y")
```

@@

## Write data for Stock Synthesis

To read in the Stock Synthesis files, first ensure you have the latest version of `r4ss`. You will need to ensure the relevant Stock Synthesis files are stored in the inst/extdata/ folder, with each species example in its own folder.

```{r readdata}
# devtools::install_github("r4ss/r4ss", dependencies = FALSE)
require(r4ss)
# source("./config/sardine_config.R") this is above for illustration

# Set species name
species <- "Pacific_sardine" # change to species_ss if we want both

# Directory with SS files
model_dir <- "Sardine_SS_files_Sep2022/"

# Name of SS data file
datfile_name <- "sardEM_3_3.dat"

stocksynthesis.data <- r4ss::SS_readdat_3.30(paste0(
  "./inst/extdata/",
  model_dir,
  datfile_name
))
```

```{r sardine-survey-spec}
# Years to survey, assuming survey is once per year
# survey_years <- survey_sample_full[(burnin+1):(burnin+nyears)] # my original
survey_years <- survey_sample_full[burnin:(burnin + nyears - 1)] # from Christine's new sardine_config.R

# Month of survey/fishing
survey_month <- 7
fishing_month <- 1
```

*Now changing catch units to tons!*

Write time series biomass (tons) and catch (tons--taken directly from truth without error) data for SS using `SS_write_ts`:

```{r SS-write-ts}

# Test writing CPUE in biomass

stocksynthesis.data <- SS_write_ts(
  ss_data_list = stocksynthesis.data,
  ts_data = list(
    survObsBiom$atoutput[fish_years],
    omlist_ss$truecatchbio_ss$atoutput[(omlist_ss$truecatchbio_ss$time / 365) %in% fish_years]
  ),
  CVs = c(
    surv_cv$cv,
    fish_cv$cv
  ),
  data_years = list((survObsBiom$time[fish_years] - survey_sample_time) / timestep + 1, fish_years),
  sampling_month = list(
    rep(survey_month, nyears),
    rep(fishing_month, nyears)
  ),
  units = c("biomass", "biomass"),
  data_type = c("CPUE", "catch"),
  fleets = c(2, 1)
)

stocksynthesis.data$CPUE

stocksynthesis.data$catch
```

Writing age composition data

```{r SS-write-comps}
# age_comp_data

# Get the age bins
age_bin_names <- names(stocksynthesis.data$agecomp)[10:length(names(stocksynthesis.data$agecomp))]
age_bins <- sub("a", "", age_bin_names)

age_comp_flat <- reformat_compositions(age_comp_data,
  round.places = 4,
  comp_type = "agecomp"
)

## Write age composition data for survey
stocksynthesis.data <- SS_write_comps(
  ss_data_list = stocksynthesis.data,
  comp_matrix = list(age_comp_flat[burnin:(burnin + nyears - 1), ]),
  data_rows = list(stocksynthesis.data$styr:(stocksynthesis.data$styr + nyears - 1)),
  sampling_month = list(rep(survey_month, nyears)),
  data_type = c("agecomp"),
  fleet_number = c(2),
  bins = list(age_bins),
  caal_bool = c(FALSE)
)

stocksynthesis.data$agecomp[, age_bin_names] <- as.data.frame(age_comp_flat)[burnin:(burnin + nyears - 1), age_bins]
```

Once we have the natlength matrix, we can munge the data into the proper CAAL and length bin format for SS

```{r SS-comps-formatting}

# Check length compositions match age compositions
# ss_length_stdsurv$natlength %>%
#  group_by(time,agecl) %>%
#  summarise(sum(atoutput))
